ms_figures

### 2024-07-24 ms_figures.Rmd
replicable data and figure directories
update file path and confirm no results changed

```{r load_data}
# Set directories
datadir <- "qa/manuscript_archive/manuscript_inputs"
outdir <- "qa/manuscript_archive/figures"
```

@@

```{r fig1de}
habitat_source_colors_v2 <- c("#F7AF75", # light orange = inland aquaculture
                              "#86ADA7", # light blue = freshwater capture
                              "#F37542", # medium orange = marine aquaculture
                              "#1B708F", # blue = marine capture
                              "black" # unknown
                          )

@@

fig1e <- ggplot() +
  geom_line(data = import_n_countries_concentration_by_source %>% 
              mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = import_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
    scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries\ncomprising ", cumulative_percent_threshold, "% imports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw() +
  theme(
    text = element_text(size = 10),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6)
  )

@@

consumer_map_df <- marine_cap_foreign_consumption %>%
  mutate(habitat_method = "Marine Capture") %>%
  bind_rows(marine_aqua_foreign_consumption %>%
              mutate(habitat_method = "Marine Aquaculture")) %>%
  bind_rows(inland_cap_foreign_consumption %>%
              mutate(habitat_method = "Inland Capture")) %>%
  bind_rows(inland_aqua_foreign_consumption %>%
              mutate(habitat_method = "Inland Aquaculture")) %>%
  group_by(consumer_iso3c, habitat_method) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup() %>%
  left_join(
    world,
    by = c("consumer_iso3c"="iso_a3")
  )

>>>>

```{r data_setup}
# Set directories
datadir <- "data"
outdir <- "figures"

# Create figures directory
if (!dir.exists(outdir)) {
  dir.create(outdir)
}
```

@@

```{r fig1de}
habitat_source_colors_v2 <- c("#1B708F", # blue = marine capture
                          "#86ADA7", # light blue = freshwater capture
                          "#F37542", # medium orange = marine aquaculture
                          "#F7AF75", # light orange = inland aquaculture
                              "black" # unknown
                          )

@@

fig1e <- ggplot() +
  geom_line(data = import_n_countries_concentration_by_source %>% 
              filter(habitat_method != "unknown") %>%
              mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = import_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
    scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries\ncomprising ", cumulative_percent_threshold, "% imports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw() +
  theme(
    text = element_text(size = 10),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6)
  )

@@

consumer_map_df <- marine_cap_foreign_consumption %>%
  mutate(habitat_method = "Marine Capture") %>%
  bind_rows(marine_aqua_foreign_consumption %>%
              mutate(habitat_method = "Marine Aquaculture")) %>%
  bind_rows(inland_cap_foreign_consumption %>%
              mutate(habitat_method = "Inland Capture")) %>%
  bind_rows(inland_aqua_foreign_consumption %>%
              mutate(habitat_method = "Inland Aquaculture")) %>%
  group_by(consumer_iso3c, habitat_method) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup() %>%
  left_join(
    world,
    by = c("consumer_iso3c"="iso_a3_eh")
  )
